Reanalyses done for the synopsis

### 2024-08-28 Rmd/thesis-reanalyses.Rmd
Added plot

---
title: "Reanalyses done for the synopsis"
author: "Niklas Karlsen"
date: "2024-08-21"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

```{r}
# load libraries
library(nlme)
library(psych)
library(dplyr)
library(pander)
```

@@

>>>>

---
title: "Reanalyses done for the synopsis"
author: "Niklas Karlsen"
date: "2024-08-28"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

Changelog

* 28.8.2024: added plot with regression line of cor(TK/TPACK) vs mTPACK

```{r}
# load libraries
library(nlme)
library(psych)
library(dplyr)
library(pander)
library(ggplot2)
```

@@

```{r}
ggplot(cor_TPACK_table[cor_TPACK_table$correlation>0.5,], aes(x=mTPACK,y=correlation)) +
  geom_point() +
  stat_smooth(method = "lm", formula = 'y ~ x', se=F,fullrange = F)
```
